This section explains the various tools and methodologies used by the three different companies that came to give a talk on their development process. The three companies are IBM, Facebook and FoodCloud. Also, these companies and compared and contrasted in the last section.

\section{IBM seminar}
\input{seminar1}

\section{Facebook seminar}
\input{seminar2}

\section{FoodCloud seminar}
\input{seminar3}

\section{Comparison of Company Seminars}
This section compares the methodology and tools used by the 3 different companies namely IBM, Facebook and FoodCloud. All the companies gave a sneak peak of their development process and their preferences for various methodologies. IBM and FoodCloud take an agile approach to building applications where Facebook leaves it to the team to decide upon whatever they think fit for the particular task. What if IBM uses Facebook way of development it might not be as productive. The reason is IBM has way more employees than Facebook and managing and tracking would become a difficult task. Also, most of the Facebook's apps run on their servers, hence they provide services. Whereas IBM does both they provide services by running software on their machines and they also provide software to be run and used by the buyer. Hence rolling out would not be possible every now and then. Also, rigorous testing is required as rolling back or updating a software running on someone else's machine is difficult and inconvenient. So, for making sure that their rollout is stable their software has to take an agile process of development.

This can be said for Facebook as well if Facebook used Agile approach throughout. Facebook has a number of data centres and most of their apps are based on distributed computing. Since they as a company provide services rather than proper software. This distributed computing makes it difficult to roll out all new features in one go and also increases chances of error. Hence, they require rollout slowly and more frequently. It also harder to roll back and find the error causing in a distributed system. One of most important thing comparing IBM, FoodCloud against Facebook is that Facebook uses reactive programming and almost have all their task automated. The reason for this is the sheer number of computers in the data centres as well as the huge code base of Facebook. Too much automation actually not needs by FoodCloud as they have much smaller scale and also they are already use very advanced and tools and services like Heroku for developing and deploying. 

All the three companies agree to the importance of Refactoring and Testing. In IBM and FoodCloud when the developers believe that the new requirement coming cannot integrate with the current design of the system and requires refactoring. The developers add refactoring as a task in their backlog and start performing them in one of the sprints. In Facebook, its more relaxed refactoring is usually done by the individual as and when they feel like it needs to be done. Since there is no specific scheme throughout they are flexible and give the developers the option to do refactoring when and how they seem fit. Testing is the major aspect of development. Facebook focuses on Unit test a lot as the integration and parallel/distributed testing of Facebook is really slow and hard. IBM and FoodCloud focused on all types of testing. IBM had another layer of Testing known as UAT which was focussed more on than other companies. In this usually, the UAT testers will go through the site as a user and see if the new features are working correctly. This is almost impossible for Facebook as their applications are too large. To this Facebook actually has tools that test code and its dependencies that are changed.

IBM, Facebook and FoodCloud all create models of software before getting into code. But none of them actually focuses too much on the UML diagram or creating models for each and every codebase. They all preferred documenting the overall structure of the system rather than going too deep in the documentation. Since software has ever changing need. Documentation actually becomes old and useless faster in such iterative programming environment.

It is quite interesting to see that each company followed the path that they believe is best for current needs. And if one tries to interchange the system, one can see it is not as effective as their current one. They all created and used tools that are right for them at that point in time. But all of the companies are very flexible in the sense to accept change. Software development has an ever changing and ever growing environment and fixating on the tools and procedure does not let you far. As no model is right model. The right model is the model that works for current needs with giving a little thought to the future.